Figures

### 2022-05-10 rmd/figures.Rmd
edit: manuscript
edit: figures

---
title: "Figures"
output: pdf_document
---

@@

**Figure 2** Ecosystem size (A) and complexity (B) have little influence on food chain length under low disturbance regime. Lines are loess curves fitted to simulated data and are colored based on omnivory. Shaded ribbons are 95% confidence intervals. Parameters for low disturbance regime: disturbance probability $p_d = 0.01$ and mean proportional mortality at headwaters $\mu_{m}=0.8$.

@@

**Figure 3** Ecosystem size (A) and complexity (B) influence food chain length under high disturbance regime. Lines are loess curves fitted to simulated data and are colored based on omnivory. Shaded ribbons are 95% confidence intervals. Parameters for high disturbance regime: disturbance probability $p_{d} = 0.01$ and mean proportional mortality at headwaters $\mu_{m}=0.8$.

>>>>

---
title: "Figures"
output: pdf_document
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

@@

**Figure 2** Ecosystem size (A) and complexity (B) have little influence on food chain length under low disturbance regime. Lines are loess curves fitted to simulated data and are colored based on omnivory. Shaded ribbons are 95% confidence intervals. Parameters for low disturbance regime: disturbance probability $p_m = 0.01$ and mean proportional mortality at headwaters $\mu_{m}=0.8$.

@@

**Figure 3** Ecosystem size (A) and complexity (B) influence food chain length under high disturbance regime. Lines are loess curves fitted to simulated data and are colored based on omnivory. Shaded ribbons are 95% confidence intervals. Parameters for high disturbance regime: disturbance probability $p_{m} = 0.01$ and mean proportional mortality at headwaters $\mu_{m}=0.8$.

### 2022-05-10 rmd/suppl_info.Rmd
Update suppl_info.Rmd
edit: figures

# Sensitivity data
load(file = here::here("output/result_stvy.RData"))
sim_sv <- sim_stvy_result
n_sim_stvy <- unique(sim_sv$n_warmup) + unique(sim_sv$n_burnin) + unique(sim_sv$n_timestep)

@@

We performed a sensitivity analysis of the trophic community simulation to identify key simulation parameters that strongly affect the relationships between food chain length and ecosystem properties (the number of habitat patches $N_{p}$ and branching probability $P_{b}$. We generated 500 sets of parameter combinations by randomly drawing values of 16 simulation parameters from uniform distributions (**Table S1**). For each parameter combination, we generated `r max(sim_stvy_result$n_rep)` branching networks with the gradients of ecosystem size ($N_p \sim Unif(10, 150)$) and complexity ($P_b \sim Unif(0.01, 0.99)$). This results in a total of `r nrow(sim_stvy_result)` simulation replicates. In each simulation replicate, we ran `r n_sim_stvy` time steps of trophic community dynamics. We obtained temporal means of food chain length for the last `r unique(sim_sv$n_timestep)` time steps. The first `r n_sim_stvy - unique(sim_sv$n_timestep)` time steps were discarded as initialization and burn-in periods.

@@

```{=tex}
\begin{align}
  u_{n} &\sim Normal(\mu_n, \sigma^2)\\
  \mu_n &= \zeta_0 + \sum_{k}{\zeta_k x_{k, n}}
\end{align}
```
where $\zeta_k~(k = 0...14)$ are the intercept and regression coefficients, and $x_{k,n}$ are the simulation parameters drawn from uniform distributions (**Table S1**). Explanatory variables were standardized to a mean of zero and a standard deviation of one, so that regression coefficients are comparable.

@@

      figure_legend <- paste0(str_to_sentence(c_text[i])," effect on food chain length and occupancies of constituent species. Rows are different response variables, and columns are different simulation scenarios. Lines and shades represent loess curves fitted to the simulated data and associated 95% confidence intervals. In this simulation, the following values of parameters were used: $\\theta$ = ", df_param$theta[k], ", $\\sigma_l$ = ", df_param$sd_disturb_lon[k], ", and $\\sigma_h$ = ", df_param$sd_disturb_source[k], ".")

>>>>

# Sensitivity data
source(here::here("code/analysis_stvy.R"))
load(file = here::here("output/result_stvy.RData"))

sim_sv <- sim_stvy_result
n_sim_stvy <- unique(sim_sv$n_warmup) + unique(sim_sv$n_burnin) + unique(sim_sv$n_timestep)

@@

We performed a sensitivity analysis of the trophic community simulation to identify key simulation parameters that strongly affect the relationships between food chain length and ecosystem properties (the number of habitat patches $N_{p}$ and branching probability $P_{b}$. We generated 500 sets of parameter combinations by randomly drawing values of `r length(attributes(fit_sense$fit[[1]]$terms)$term.label)` simulation parameters from uniform distributions (**Table S1**). For each parameter combination, we generated `r max(sim_sv$n_rep)` branching networks with the gradients of ecosystem size ($N_p \sim Unif(10, 150)$) and complexity ($P_b \sim Unif(0.01, 0.99)$). This results in a total of `r nrow(sim_sv)` simulation replicates. We ran `r n_sim_stvy` time steps of trophic community dynamics in each simulation replicate. We obtained temporal means of food chain length for the last `r unique(sim_sv$n_timestep)` time steps. The first `r n_sim_stvy - unique(sim_sv$n_timestep)` time steps were discarded as initialization and burn-in periods.

@@

```{=tex}
\begin{align}
  u_{n} &\sim Normal(\mu_n, \sigma^2)\\
  \mu_n &= \zeta_0 + \sum_{k}{\zeta_k x_{k, n}}
\end{align}
```
where $\zeta_k$ are the intercept and regression coefficients, and $x_{k,n}$ are the simulation parameters drawn from uniform distributions (**Table S1**). Response and explanatory variables were standardized to a mean of zero and a standard deviation of one so that regression coefficients are comparable.

@@

      figure_legend <- paste0(str_to_sentence(c_text[i])," effect on food chain length and occupancies of constituent species (proportion of habitat patches occupied). Rows are different response variables, and columns are different simulation scenarios. Lines and shades represent loess curves fitted to the simulated data and associated 95% confidence intervals. In this simulation, the following values of parameters were used: $\\theta$ = ", df_param$theta[k], ", $\\sigma_l$ = ", df_param$sd_disturb_lon[k], ", and $\\sigma_h$ = ", df_param$sd_disturb_source[k], ".")
